\item {{Barat}, S.}, {{D\'esert}, J.~M.}, {{Vazan}, A.}, and 12 colleagues, 2024, ``The metal-poor atmosphere of a potential Sub-Neptune progenitor,'' accepted to \textit{Nature Astronomy}.

\item {{Colman}, I. L.}, {{Angus}, R.}, {\bf{{David}, T.~J}}, and 3 colleagues, 2024, ``{Methods for the Detection of Stellar Rotation Periods in Individual TESS Sectors and Results from the Prime Mission},'' \textit{\aj}, 167, 189. \href{https://ui.adsabs.harvard.edu/abs/2024AJ....167..189C}{[ADS]}.

\item {{Tyler}, D.}, {{Petigura}, E. A.}, {{Oklop{\v{c}}i{\'c}}, A.}, and {\bf{{David}, T.~J}}, 2024, ``{WASP-69b's Escaping Envelope Is Confined to a Tail Extending at Least 7 R$_p$},'' \textit{\apj}, 960, 123. \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...960..123T}{[ADS]}.

\item {{Blunt}, S.}, {{Carvalho}, A.}, {\bf{{David}, T. J.}}, and 23 colleagues, 2023, ``{Overfitting Affects the Reliability of Radial Velocity Mass Estimates of the V1298 Tau Planets},'' \textit{\aj}, 166, 62. \href{https://ui.adsabs.harvard.edu/abs/2023AJ....166...62B}{[ADS]}.

% \item {{Chance}, Q.}, {{Foreman-Mackey}, D.}, {{Ballard}, S.}, and 3 colleagues, 2022, ``{paired: A Statistical Framework for Determining Stellar Binarity with Gaia RVs. I. Planet Hosting Binaries},'' arXiv:2206.11275. \href{https://ui.adsabs.harvard.edu/abs/2022arXiv220611275C}{[ADS]}.

\item {Jaehnig, K.}, {Price-Whelan, A.~M.}, {Foreman-Mackey, D.} and 5 colleagues, ``{Spectroscopic eclipsing binary orbital parameter estimation with TESS and APOGEE}," submitted to AAS Journals.

\item {{Chance}, Q., {Foreman-Mackey}, D.,  {Ballard}, S., and 3 colleagues}, 2022, ``{paired: A Statistical Framework for Determining Stellar Binarity with Gaia RVs. I. Planet Hosting Binaries}," submitted to \textit{The Astrophysical Journal}. \href{https://ui.adsabs.harvard.edu/abs/2022arXiv220611275C/abstract}{[ADS]}.


\item {{Thao}, P. C.}, {{Mann}, A. W.}, {{Gao}, P.}, and 10 colleagues, 2023, ``{Hazy with a Chance of Star Spots: Constraining the Atmosphere of Young Planet K2-33b},'' \textit{\aj}, 165, 23. \href{https://ui.adsabs.harvard.edu/abs/2023AJ....165...23T}{[ADS]}.

\item {{Lu}, Y. L.}, {{Curtis}, J. L.}, {{Angus}, R.}, and 2 colleagues, 2022, ``{Bridging the Gap-The Disappearance of the Intermediate Period Gap for Fully Convective Stars, Uncovered by New ZTF Rotation Periods},'' \textit{\aj}, 164, 251. \href{https://ui.adsabs.harvard.edu/abs/2022AJ....164..251L}{[ADS]}.

\item {{\bf{David}, T. J.}}, {{Angus}, R.}, {{Curtis}, J. L.}, and 5 colleagues, 2022, ``{Further Evidence of Modified Spin-down in Sun-like Stars: Pileups in the Temperature-Period Distribution},'' \textit{\apj}, 933, 114. \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...933..114D}{[ADS]}.

\item {{Johnson}, M. C.}, {{\bf{David}, T. J.}}, {{Petigura}, E. A.}, and 22 colleagues, 2022, ``{An Aligned Orbit for the Young Planet V1298 Tau b},'' \textit{\aj}, 163, 247. \href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..247J}{[ADS]}.

\item {{Hedges}, C., {Hughes}, A., {Zhou}, G., and 49 colleagues}, 2022, ``{Erratum: ``TOI-2076 and TOI-1807: Two Young, Comoving Planetary Systems within 50 pc Identified by TESS that are Ideal Candidates for Further Follow Up" (2021, AJ, 162, 54)}," \textit{The Astronomical Journal}, 163, 143. \href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..143H/abstract}{[ADS]}.

\item {{Feinstein}, A.~D., \textbf{{David}, T.~J.}, {Montet}, B.~T., and 3 colleagues}, 2022, ``{V1298 Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298 Tau e}," \textit{The Astrophysical Journal Letters}, 925, L2. \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...925L...2F/abstract}{[ADS]}.

\item {{Hedges}, C., {Hughes}, A., {Zhou}, G., and 49 colleagues}, 2021, ``{Erratum: ``TOI-2076 and TOI-1807: Two Young, Comoving Planetary Systems within 50 pc Identified by TESS that are Ideal Candidates for Further Follow Up" (2021, AJ, 162, 54)}," \textit{The Astronomical Journal}, 162, 305. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....162..305H/abstract}{[ADS]}.

\item {{Vissapragada}, S., {Stef{\'a}nsson}, G., {Greklek-McKeon}, M., and 28 colleagues}, 2021, ``{A Search for Planetary Metastable Helium Absorption in the V1298 Tau System}," \textit{The Astronomical Journal}, 162, 222. 
\href{https://ui.adsabs.harvard.edu/abs/2021AJ....162..222V/abstract}{[ADS]}.

\item {{Feinstein}, A., {Montet}, B., {Johnson}, M., and 5 colleagues}, 2021, ``{H-$\alpha$ and Ca II Infrared Triplet Variations During a Transit of the 23 Myr Planet V1298 Tau c}," \textit{The Astronomical Journal}, 162, 213. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....162..213F/abstract}{[ADS]}.

\item {{Rebull}, L., {Stauffer}, J.~R., {Cody}, A.~M., and 4 colleagues}, 2021, ``{Erratum: ``Rotation of Low-mass Stars in Taurus with K2'' (2020, AJ, 159, 273)}," \textit{The Astronomical Journal}, 162, 172. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....162..172R/abstract}{[ADS]}.

\item {{Hedges}, C., {Hughes}, A., {Zhou}, G., {\bf {David}, T.~J.}, and 43 colleagues}, 2021, ``{TOI-2076 and TOI-1807: Two Young, Comoving Planetary Systems within 50 pc Identified by TESS that are Ideal Candidates for Further Follow Up}," \textit{The Astronomical Journal}, 162, 54. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....162...54H}{[ADS]}.

\item {{Foreman-Mackey}, D., {Luger}, R., {Agol}, E., and 13 colleagues}, 2021, ``{exoplanet: Gradient-based probabilistic inference for exoplanet data \& other astronomical time series}," \textit{The Journal of Open Source Software}, 6, 3285. \href{https://ui.adsabs.harvard.edu/abs/2021JOSS....6.3285F}{[ADS]}.

\item {\bf {David}, T.~J.}, {Contardo}, G., {Sandoval}, A., and 7 colleagues, 2020, ``{Evolution of the Exoplanet Size Distribution: Forming Large Super-Earths Over Billions of Years}," \textit{The Astronomical Journal}, 161, 265. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....161..265D/abstract}{[ADS]}.

\item {Sandoval}, A., {Contardo}, G., and {\bf {David}, T.~J.}, 2020, ``{The Influence of Age on the Relative Frequency of Super-Earths and Sub-Neptunes}," \textit{The Astrophysical Journal}, 911, 117. \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...911..117S}{[ADS]}.

\item {Lu}, Y., {Angus}, R., {Curtis}, J.~L., and 2 colleagues, 2021, ``{Gyro-Kinematic Ages for around 30,000 Kepler Stars}," \textit{The Astronomical Journal}, 161, 189. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....161..189L/abstract}{[ADS]}.

\item {Matthews}, E.~C., {Hinkley}, S., {Stapelfeldt}, K., and 8 colleagues, 2020, ``{Three new late-type stellar companions to very dusty WISE debris disks identified with VLT/SPHERE imaging}," \textit{The Astronomical Journal}, 161, 78. \href{https://ui.adsabs.harvard.edu/abs/2021AJ....161...78M/abstract}{[ADS]}.

\item {van Dam}, D.~M., {Kenworthy}, M.~A., {\bf {David}, T.~J.}, and 21 colleagues, 2020, ``{An Asymmetric Eclipse Seen toward the Pre-main-sequence Binary System V928 Tau}," \textit{The Astronomical Journal}, 160, 285. \href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..285V/abstract}{[ADS]}.

\item {Gagn{\'e}}, J., {\bf {David}, T.~J.}, {Mamajek}, E.~E., and 3 colleagues, 2020, ``{The {\ensuremath{\mu}} Tau Association: A 60 Myr Old Coeval Group at 150 pc from the Sun}," \textit{The Astrophysical Journal}, 903, 96. \href{https://ui.adsabs.harvard.edu/abs/2020ApJ...903...96G/abstract}{[ADS]}.

\item {Stauffer}, J.~R., {Barrado}, D., {\bf {David}, T.~J.} and 7 colleagues, 2020, ``{Pleiades or Not? Resolving the Status of the Lithium-rich M Dwarfs HHJ 339 and HHJ 430}," \textit{The Astronomical Journal}, 160, 30. \href{https://ui.adsabs.harvard.edu/abs/2020AJ....160...30S/abstract}{[ADS]}.

\item {Rebull}, L.~M., {Stauffer}, J.~R., {Cody}, A.~M. and 4 colleagues, 2020, ``{Rotation of Low-mass Stars in Taurus with K2}," \textit{The Astronomical Journal}, 159, 273. \href{https://ui.adsabs.harvard.edu/abs/2020AJ....159..273R/abstract}{[ADS]}.

\item {\bf {David}, T.~J.}, {Petigura}, E.~A., {Luger}, R., and 4 colleagues, 2019, ``{Four newborn planets transiting the young solar analog V1298 Tau}," \textit{The Astrophysical Journal Letters}, 885, L12. \href{https://ui.adsabs.harvard.edu/abs/2019arXiv191004563D/abstract}{[ADS]}.

\item {Hippke}, M., \textbf{{David}, T~.J.}, {Mulders}, G.~D., and {Heller}, R., 2019, ``{W\={o}tan: Comprehensive time-series de-trending in Python},''\textit{The Astronomical Journal}, 158, 143. \href{https://ui.adsabs.harvard.edu/abs/2019AJ....158..143H/abstract}{[ADS]}.

\item {\bf {David}, T.~J.}, {Cody}, A.~M., {Hedges}, C.~L., and 14 colleagues, 2019, ``{A warm Jupiter-sized planet transiting the pre-main sequence star V1298 Tau},", \textit{The Astronomical Journal}, 158, 79. \href{https://ui.adsabs.harvard.edu/abs/2019AJ....158...79D/abstract}{[ADS]}.

\item {Beichman}, C.~A., {Hirano}, {\bf {David}, T.~J.}, and 9 colleagues, 2019, ``{A Mass Limit for the Young Transiting Planet V1298 Tau b},", \textit{Research Notes of the AAS}, 3, 6. \href{https://iopscience.iop.org/article/10.3847/2515-5172/ab2c9d}{[IOP]}.

\item {\bf {David}, T.~J.}, {Hillenbrand}, L.~A., {Gillen}, E., and 4 colleagues, 2019, ``{Age Determination in Upper Scorpius with Eclipsing Binaries}," \textit{The Astrophysical Journal}, 872, 161.\ \href{https://ui.adsabs.harvard.edu/abs/2019ApJ...872..161D/abstract}{[ADS]}.

\item {Mellon}, S.~N., {Mamajek}, E.~E., Zwintz, K., and 11 colleagues, 2019, ``{Discovery of $\delta$ Scuti Pulsations in the Young Hybrid Debris Disk Star HD 156623}," \textit{The Astrophysical Journal}, 870, 36. \href{https://ui.adsabs.harvard.edu/#abs/2019ApJ...870...36M/}{[ADS]}.

\item {\bf {David}, T.~J.}, {Mamajek}, E.~E., {Vanderburg}, A., and 19 colleagues, 2018, ``{Discovery of a Transiting Adolescent Sub-Neptune Exoplanet with K2}," \aj, 156, 302.  \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....156..302D/}{[ADS]}. 

\item {Stauffer}, J.~R., {Rebull}, L.~M., {Cody}, A.~M., and 5 colleagues, 2018, ``{The Rotational Evolution of Young, Binary M Dwarfs}," \aj, 156, 275. \href{https://ui.adsabs.harvard.edu/abs/2018AJ....156..275S/abstract}{[ADS]}.

\item {Crossfield}, I.~J.~M., {Guerrero}, N., {\bf {David}, T.~J.}, and 38 colleagues, 2018, ``{A TESS Dress Rehearsal: Planetary Candidates and Variables from K2 Campaign 17},'' \apjs, 239, 5. \href{https://ui.adsabs.harvard.edu/#abs/2018arXiv180603127C}{[ADS]}.

\item {Peterson}, M.~S., {Benneke}, B., {\bf {David}, T.~J.}, and 21 colleagues, 2018, ``{A 2 R $_{{\ensuremath{\oplus}}}$ Planet Orbiting the Bright Nearby K Dwarf Wolf 503}," \aj, 156, 188. \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....156..188P}{[ADS]}.

\item {Matthews}, E., {Hinkley}, S., {Vigan}, A., and 10 colleagues, 2018, ``{Constraining the presence of giant planets in two-belt debris disc systems with VLT/SPHERE direct imaging and dynamical arguments}," \mnras, 480, 2757. \href{https://ui.adsabs.harvard.edu/#abs/2018MNRAS.480.2757M}{[ADS]}.

\item {Wang}, J., {\bf {David}, T.~J.}, {Hillenbrand}, L.~A., and 3 colleagues, 2018, ``{EPIC 203868608: A Low-mass Quadruple Star System in the Upper Scorpius OB Association},'' \apj, 865, 141. \href{https://ui.adsabs.harvard.edu/#abs/2018ApJ...865..141W}{[ADS]}.

\item {\bf {\bf David, T.}~J.}, {Crossfield}, I.~J.~M., {Benneke}, B., and 14 colleagues, 2018, ``{Three Small Planets Transiting the Bright Young Field Star K2-233}," \textit{The Astronomical Journal}, 155, 222.\ \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....155..222D/}{[ADS]}. 

\item {Rebull}, L.~M., {Stauffer}, J.~R., {Cody}, A.~M., and 3 colleagues, 2018, ``{Rotation of Low-mass Stars in Upper Scorpius and {\ensuremath{\rho}} Ophiuchus with K2}," \aj, 155, 196. \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....155..196R}{[ADS]}.

\item {Stauffer}, J.~R., {Rebull}, L.~M., {\bf {David}, T.~J.}, and 8 colleagues, 2018, ``{More Rapidly Rotating PMS M Dwarfs with Light Curves Suggestive of Orbiting Clouds of Material}," \aj, 155, 63. \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....155...63S}{[ADS]}.

\item {\bf {David}, T.~J.}, 2018, ``{On the Evolutionary Pathways of Stars and Extrasolar Planets}," Ph.D. Thesis, \textit{California Institute of Technology}. \href{https://ui.adsabs.harvard.edu/abs/2018PhDT........38D/abstract}{[ADS]}.

\item {Ciardi}, D.~R., {Crossfield}, I.~J.~M., {Feinstein}, A.~D., and 14 colleagues, 2018, ``{K2-136: A Binary System in the Hyades Cluster Hosting a Neptune-sized Planet}," \aj, 155, 10. \href{https://ui.adsabs.harvard.edu/#abs/2018AJ....155...10C}{[ADS]}.

\item {Gillen}, E., {Hillenbrand}, L.~A., {\bf {David}, T.~J.}, and 5 colleagues, 2017 ``{New Low-mass Eclipsing Binary Systems in Praesepe Discovered by K2}," \apj, 849, 11. \href{https://ui.adsabs.harvard.edu/#abs/2017ApJ...849...11G}{[ADS]}.

\item {Pepper}, J., {Gillen}, E., {Parviainen}, H., and 11 colleagues, 2017, ``{A Low-mass Exoplanet Candidate Detected by K2 Transiting the Praesepe M Dwarf JS 183}," \aj, 153, 177. \href{https://ui.adsabs.harvard.edu/#abs/2017AJ....153..177P}{[ADS]}.

\item {Stauffer}, J~.R., {Collier Cameron}, A., {Jardine}, M., and 8 colleagues, 2017, ``{Orbiting Clouds of Material at the Keplerian Co-rotation Radius of Rapidly Rotating Low-mass WTTs in Upper Sco}," \aj, 153, 152. \href{https://ui.adsabs.harvard.edu/#abs/2017AJ....153..152S}{[ADS]}.

\item {Cody}, A.~M., {Hillenbrand}, L.~A., {\bf {David}, T.~J.}, and 3 colleagues, 2017, ``{A Continuum of Accretion Burst Behavior in Young Stars Observed by K2}," \apj, 836, 41. \href{https://ui.adsabs.harvard.edu/#abs/2017ApJ...836...41C}{[ADS]}.

\item {\bf {\bf David, T.}~J.}, {Petigura}, E.~A., {Hillenbrand}, L.~A., and 14 colleagues, 2017, ``{A Transient Transit Signature Associated with the Young Star RIK-210}," \textit{The Astrophysical Journal}, 835, 168.\ \href{https://ui.adsabs.harvard.edu/#abs/2017ApJ...835..168D/}{[ADS]}. 

\item {Obermeier}, C., {Henning}, T., {Schlieder}, J.~E., and 21 colleagues, 2016, ``{K2 Discovers a Busy Bee: An Unusual Transiting Neptune Found in the Beehive Cluster}," \aj, 152, 223. \href{https://ui.adsabs.harvard.edu/#abs/2016AJ....152..223O}{[ADS]}.

\item {Stauffer}, J.~R., {Rebull}, L.~M., {Bouvier}, J., and 15 colleagues, 2016, ``{Rotation in the Pleiades with K2. III. Speculations on Origins and Evolution}," \aj, 152, 115. \href{https://ui.adsabs.harvard.edu/#abs/2016AJ....152..115S}{[ADS]}. 

\item {\bf {\bf David, T.}~J.}, {Hillenbrand}, L.~A., {Petigura}, E.~A., and 10 colleagues, 2016, ``{A Neptune-sized transiting planet closely orbiting a 5-10-million-year-old star}," \nature, 534, 658.\ \href{https://ui.adsabs.harvard.edu/#abs/2016Natur.534..658D/}{[ADS]}. 

\item {\bf {\bf David, T.}~J.}, {Conroy}, K.~E., {Hillenbrand}, L.~A., and 7 colleagues, 2016, ``{New Pleiades Eclipsing Binaries and a Hyades Transiting System Identified by K2}," \aj, 151, 112.\ \href{https://ui.adsabs.harvard.edu/#abs/2016AJ....151..112D/}{[ADS]}.

\item {\bf {\bf David, T.}~J.}, {Hillenbrand}, L.~A., {Cody}, A.~M., and 5 colleagues, 2016, ``{K2 Discovery of Young Eclipsing Binaries in Upper Scorpius: Direct Mass and Radius Determinations for the Lowest Mass Stars and Initial Characterization of an Eclipsing Brown Dwarf Binary}," \apj, 816, 21.\ \href{https://ui.adsabs.harvard.edu/#abs/2016ApJ...816...21D/}{[ADS]}.

\item {\bf {\bf David, T.}~J.}, {Stauffer}, J.~R., {Hillenbrand}, L.~A., and 16 colleagues, 2015, ``{HII 2407: An Eclipsing Binary Revealed By K2 Observations of the Pleiades}," \apj, 814, 62.\ \href{https://ui.adsabs.harvard.edu/#abs/2015ApJ...814...62D/}{[ADS]}.

\item {Mawet}, D., {\bf {David}, T.~J.}, {Bottom}, M., and 7 colleagues, 2015, ``{Discovery of a Low-mass Companion Around HR 3549}," \apj, 811, 10. \href{https://ui.adsabs.harvard.edu/#abs/2015ApJ...811..103M}{[ADS]}.

\item {\bf {\bf David, T.}~J.}, and {Hillenbrand}, L.~A., 2015, ``{The Ages of Early-type Stars: Str{\"o}mgren Photometric Methods Calibrated, Validated, Tested, and Applied to Hosts and Prospective Hosts of Directly Imaged Exoplanets}," \apj, 804, 146.\ \href{https://ui.adsabs.harvard.edu/#abs/2015ApJ...804..146D/}{[ADS]}.

\item {Hinkley}, S., {Pueyo}, L., {Faherty}, J.~K., and 29 colleagues, 2013, ``{The {\ensuremath{\kappa}} Andromedae System: New Constraints on the Companion Mass, System Age, and Further Multiplicity}," \apj, 779, 153. \href{https://ui.adsabs.harvard.edu/#abs/2013ApJ...779..153H}{[ADS]}.

\item {Sheffield}, A.~A., {Majewski}, S.~R., {Johnston}, K.~V., and 10 colleagues, 2012, ``{Identifying Contributions to the Stellar Halo from Accreted, Kicked-out, and In Situ Populations}," \apj, 761, 161. \href{https://ui.adsabs.harvard.edu/#abs/2012ApJ...761..161S}{[ADS]}. 